Quantitative Evaluation of Touch-Screen Performance with Transition Matrix Measures

### 2015-08-31 flux-entropy-paper/flux-entropy-paper.tex
added last two analysis sections

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/flux-through-time}
  \caption{Distribution flux values of sessions through time.
    Different performance styles are visible as clusters of similar
    flux regardless of performance context.
    \label{fig:flux-through-time}}
\end{figure}

>>>>

While the interaction session in our corpus have many different
contexts, they are all part of a program of artistic and HCI research
that has evolved over time. Figures \ref{fig:flux-through-time} and
\ref{fig:entropy-through-time} show the values of flux and entropy for
each session in the corpus. Over the course of this research program,
different ensembles and different activities have been emphasised,
some of these differences can be seen as clusters of performances with
similar flux and entropy in the two plots. For instance, the earliest
series of rehearsals and performances had flux between 0.05 and 0.15,
while the period of activity after July 2014 had flux between 0.1 and
0.25. This change corresponded with an intensive series of study
sessions and rehearsals where the participants developed a more
fluctuating style of performance. The entropy between these two
periods, however, remains at a similiar level, showing the the space
of available gestures that the performers explored was more constant.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/flux-through-time}
  \caption{Distribution of flux values of sessions through time.
    Different performance styles are visible as clusters of similar
    flux regardless of performance context.
    \label{fig:flux-through-time}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/entropy-through-time}
  \caption{Distribution of entropy values of sessions through time.
    \label{fig:entropy-through-time}}
\end{figure}
